Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-05-22 WSSSPE2_report/WSSSPE2_review.tex
Update WSSSPE2_review.tex

\begin{enumerate}
\item \textbf{Colin Venters: The Nebuchadnezzar Effect: Dreaming of Sustainable
Software through Sustainable Software Architectures~\cite{Venters_poster}.}
Venters proposed that sustainable software is a composite, first-class,
non-functional requirement (NFR) that is at a minimum a measure of a system's
maintainability and extensibility, but may also include other NFRs such as
efficiency (e.g., energy, cost), interoperability, portability, reusability,
scalability, and usability. To achieve technically sustainable software, Venters
suggested that software architectures are fundamental as they are the primary
carrier of system NFRs, i.e., pre-system understanding; and influence how
developers are able to understand, analyze, extend, test, and maintain a
software system, i.e., post-deployment system understanding. In addition,
Venters highlighted that sustainability of software architectures needs to be
addressed to endure different types of change and evolution in order to mitigate
architectural drift, erosion, and knowledge vaporization.

@@

>>>>

\begin{enumerate}
\item \textbf{Colin C. Venters: The Nebuchadnezzar Effect: Dreaming of Sustainable
Software through Sustainable Software Architectures~\cite{Venters_poster}.}
Venters proposed that sustainable software is a composite, first-class,
non-functional requirement (NFR) that is at a minimum a measure of a system's
maintainability and extensibility, but may also include other NFRs such as
efficiency (e.g., energy, cost), interoperability, portability, reusability,
scalability, and usability. To achieve technically sustainable software, Venters
suggested that software architectures are fundamental as they are the primary
carrier of system NFRs, i.e., pre-system understanding; and influence how
developers are able to understand, analyze, extend, test, and maintain a
software system, i.e., post-deployment system understanding. In addition,
Venters highlighted that sustainability of software architectures needs to be
addressed to endure different types of change and evolution in order to mitigate
architectural drift, erosion, and knowledge vaporization.

@@

\todo{short intro to group here}
Six papers were categorized under the theme of Exploring Sustainability. The group included four of the authors from the six papers submitted and an additional number of participants who expressed an interest in the theme at the workshop. Each paper had a different perspective on the concept of sustainability, which ranged from the sustainment of communities to defining sustainability as a first-class, composite non-functional requirement.
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Discussion and Actions}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
